Disk Winds Matter: Simulating the Optical Spectra of Cataclysmic Variables

### 2014-09-02 draft.tex
Version to send first iteration

\py has previously been tested against a number of radiative transfer and
photoionization codes. Comparisons of ionization balance with \cld \citep{cloudy2013} 
can be found in LK02 and H13 and show excellent agreement. We have also conducted comparisons
of ionization and spectral synthesis with the supernova code \textsc{Tardis.} \tar is described by
\cite{kerzendorfsim}, and the spectral comparisons can be found therein.
In addition to these code validation efforts, we have also conducted tests of
the macro atom scheme in \py to verify that it does indeed solve for level populations correctly
and produces the expected level emissivities. Figure~\ref{tests} shows good agreement with 
Case B, l-mixed calculations by \cite{seaton1959}, and level
population calcaultions with \textsc{Tardis.}

>>>>

\py has previously been tested against a number of radiative transfer and
photoionization codes. Comparisons of ionization balance with \cld \citep{cloudy2013} 
can be found in LK02 and H13 and show excellent agreement. We have also conducted comparisons
of ionization and spectral synthesis with the supernova code \textsc{Tardis.} \tar is described by
\cite{kerzendorfsim}, and the spectral comparisons can be found therein.
In addition to these code validation efforts, we have also conducted tests of
the macro atom scheme in \py to verify that it does indeed solve for level populations correctly
and produces the expected level emissivities. Figure~\ref{tests} shows good agreement with 
l-mixed Balmer decrements in the Case B limit by \cite{seaton1959}, and 
also compares He\textsc{i} level populations with \textsc{Tardis.}
